---
title: "Explore more realistic dosing scenarios"
author: "Andy Stein"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---
### Headers
```{r, warning=FALSE}
suppressMessages(source("ams_initialize_script.R"))
source("AFIRT_calculation.R")
```

### Set initial parameters and functions
Here use doses ranging from 0.1-100 mg/kg or `r signif(.1*scale.mpk2nmol,2)`-`r signif(100*scale.mpk2nmol,2)` nmol because this is a more realistic dose range to consider. 

```{r}
dose.nmol.range = lseq(.1,100,7)*scale.mpk2nmol

model = ivsc_4cmtct_shedct()

tmax = 26*7 #days
tau  = 21   #days
compartment = 2
```
### Atezolizumab (Membrane-bound Target)
Atezolizumab is dosed at 1200 mg or `r 1200*scale.mg2nmol` nmol.  Andy doesn't currently know the kon and koff rates for atezolizumab.  He guessed koff = 3/d, but it could be 10 faster.

```{r, warning=FALSE}
param.as.double = read.param.file("../data/ModelF_Atezolizumab_Params.xlsx")
p.atezo         = as.data.frame(t(param.as.double))

param.to.change = "dose"
param.to.change.range = dose.nmol.range
dose.nmol = median(dose.nmol.range)
soluble = FALSE

df_compare = compare.thy.sim(model = model,
                               param.as.double = param.as.double,
                               dose.nmol = dose.nmol,
                               tmax = tmax,
                               tau  = tau,
                               compartment = compartment,
                               param.to.change = param.to.change,
                               param.to.change.range = param.to.change.range,
                               soluble = soluble)

d.long = df_compare %>%
  select(type,dose=param.to.change,Tacc.tum,B,Cavg1,Cavg3,Cmin,AFIRT,TFIRT) %>%
  gather(key=param,value,-c(type,dose))

g = ggplot(data=d.long,aes(x=dose,y=value,color=type,linetype=type))
g = g + geom_line()
g = g + scale.y.log10()
g = g + scale.x.log10()
g = g + facet_wrap(~param,scales="free_y")
print(g)
```

### Atezo with large k13DM - theory gets worse

```{r, warnings=FALSE}
#param.as.double["kshedDM3"] = 0
param.as.double["k13DM"] = 50

df_compare = compare.thy.sim(model = model,
                               param.as.double = param.as.double,
                               dose.nmol = dose.nmol,
                               tmax = tmax,
                               tau  = tau,
                               compartment = compartment,
                               param.to.change = param.to.change,
                               param.to.change.range = param.to.change.range,
                               soluble = soluble)

d.long = df_compare %>%
  select(type,dose=param.to.change,Tacc.tum,B,Cavg1,Cavg3,Cmin,AFIRT,TFIRT) %>%
  gather(key=param,value,-c(type,dose))

g = ggplot(data=d.long,aes(x=dose,y=value,color=type,linetype=type))
g = g + geom_line()
g = g + scale.y.log10()
g = g + scale.x.log10()
g = g + facet_wrap(~param,scales = "free_y")
print(g)
```


### Bevacizumab (Soluble Target)
```{r, warning=FALSE}
param.as.double = read.param.file("../data/ModelF_Bevacizumab_Params.xlsx")
p.beva         = as.data.frame(t(param.as.double))

out = simulation(model=model, param.as.double=param.as.double, 
      dose.nmol=max(dose.nmol.range), tmax=tmax, tau=tau) %>%
  select(time,D1,D3,S1,DS1,S3,DS3,Sfree.pct) %>%
  gather(cmt,value,-c(time))

g = ggplot(out,aes(x=time,y=value,group=cmt,color=cmt))
g = g + geom_line()
g = g + scale.y.log10()
g = g + facet_wrap(~cmt, scales="free_y")
g = xscale("w27",increment = 3)
print(g)

param.to.change = "dose"
param.to.change.range = dose.nmol.range
dose.nmol = median(dose.nmol.range)
soluble = TRUE

df_compare = compare.thy.sim(model = model,
                               param.as.double = param.as.double,
                               dose.nmol = dose.nmol,
                               tmax = tmax,
                               tau  = tau,
                               compartment = compartment,
                               param.to.change = param.to.change,
                               param.to.change.range = param.to.change.range,
                               soluble = soluble)

d.long = df_compare %>%
  select(type,dose=param.to.change,Tacc.tum,B,Cavg1,Cavg3,Cmin,AFIRT,TFIRT) %>%
  gather(key=param,value,-c(type,dose))

g = ggplot(data=d.long,aes(x=dose,y=value,color=type,linetype=type))
g = g + geom_line()
g = g + scale.y.log10()
g = g + scale.x.log10()
g = g + facet_wrap(~param,scales = "free_y")
print(g)
```

### Bevacizumab - try setting params to zero to see if it helps
If k13DS is set to zero, the results are more accurate.

```{r, warnings=FALSE}
#param.as.double["kshedDM3"] = 0
param.as.double["k13DS"] = 0

df_compare = compare.thy.sim(model = model,
                               param.as.double = param.as.double,
                               dose.nmol = dose.nmol,
                               tmax = tmax,
                               tau  = tau,
                               compartment = compartment,
                               param.to.change = param.to.change,
                               param.to.change.range = param.to.change.range,
                               soluble = soluble)

d.long = df_compare %>%
  select(type,dose=param.to.change,Tacc.tum,B,Cavg1,Cavg3,Cmin,AFIRT,TFIRT) %>%
  gather(key=param,value,-c(type,dose))

g = ggplot(data=d.long,aes(x=dose,y=value,color=type,linetype=type))
g = g + geom_line()
g = g + scale.y.log10()
g = g + scale.x.log10()
g = g + facet_wrap(~param,scales = "free_y")
print(g)
```
