---
title: "Task11_Jumps_In_Sensitivity_Analysis"
author: "Hongshan Li"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---
In the first plot of "Task05_Sensistivity_Analysis_pt5.Rmd", it is strange that
AFIRT.sim jumps as ksynM3 changes from the 4th value to the 5th value
(Take pemb as an example), because
as indicated in the AFTIR derivation part of the writeup, Keq does not depend
on ksynM3, i.e. AFTIR does not depend on ksynM3. This is illustrated in the 
plots of AFTIR.Kssd, AFTIR.Kss, and AFTIR.Kd, where the dependences on ksynM3 are 
barely noticeable. 

This indicates that our approximation of Keq does not apply when ksynM3 is large 
(or when target concentration is large). By definition
\[
    K_{ssd, mem} = \frac{D_3\cdot M_3}{DM_3}
\]
so it is reasonable that as ksynM3 gets big, $K_{ssd, mem}$ gets big. Then, we will
not be able assume (2.2.20 of the writeup)
\[
    \frac{T_3}{T_{3tot}} = \frac{K_{eq}}{K_{eq} + D_3} \sim
    \frac{K_{eq}}{D_3}
\]

Therefore, in order for the above approximation to be true, we will have to increase
the dose for large ksynM3, so that $Keq << D_3$. 

I will run a sensitivity analysis on ksynM3 with the same range of value as in
Task05, but I will significantly increase the dose. Then, we should be able to  
see better agreement between theory and simulation


```{r, warning=FALSE}
suppressMessages(source("ams_initialize_script.R"))
suppressMessages(source("ams_initialize_script.R"))
model = ivsc_4cmtct_shedct(target=TRUE)

# test on Pemb, and run senstivity analysis on ksynM3
drug = "Pembrolizumab"
drug.path = paste0("../data/ModelF_", drug, "_Params.xlsx")
parameter = "ksynM3"

# Set global variables
tmax = 26*7
tau = 21
compartment = 2

# Load model parameters for pemb
param.as.double = read.param.file(drug.path)
df_param = as.data.frame(t(param.as.double))

# grep ksynM3
ksynM3.init = df_param["ksynM3"]

# set the range for ksynM3
ksynM3.range = data.frame(lapply(ksynM3.init, function(x) lseq(x*0.01, x*100, 7)))
```
With low dose
```{r}
dose.nmol = scale.mpk2nmol
# run the sensitivity analysis on the above range
AFIRT = compare.thy.sim(model=model,
                    param.as.double=param.as.double,
                    dose.nmol = dose.nmol,
                    tmax = tmax,
                    tau = tau,
                    compartment = compartment,
                    param.to.change = 'ksynM3',
                    param.to.change.range = ksynM3.range[[1]],
                    soluble = FALSE)

# get the relevant data from the above frame
relevant = AFIRT[c("fold.change.param", "AFIRT.Kssd", "AFIRT.Kss","AFIRT.Kd", "AFIRT.sim", "param")]

relevant = relevant %>% 
  gather(key, AFIRT.value, -param, -fold.change.param) %>%
  filter(!is.na(AFIRT.value))

g = ggplot(relevant, aes(fold.change.param, AFIRT.value, color=key, linetype=key)) +
  scale.x.log10() + 
  scale.y.log10() + 
  geom_line() + 
  geom_point()

print(g)
```

With high dose (100 times higher)
```{r}
dose.nmol = 1000*scale.mpk2nmol
# run the sensitivity analysis on the above range
AFIRT = compare.thy.sim(model=model,
                    param.as.double=param.as.double,
                    dose.nmol = dose.nmol,
                    tmax = tmax,
                    tau = tau,
                    compartment = compartment,
                    param.to.change = 'ksynM3',
                    param.to.change.range = ksynM3.range[[1]],
                    soluble = FALSE)

# get the relevant data from the above frame
relevant = AFIRT[c("fold.change.param", "AFIRT.Kssd", "AFIRT.Kss","AFIRT.Kd", "AFIRT.sim", "param")]

relevant = relevant %>% 
  gather(key, AFIRT.value, -param, -fold.change.param) %>%
  filter(!is.na(AFIRT.value))

g = ggplot(relevant, aes(fold.change.param, AFIRT.value, color=key, linetype=key)) +
  scale.x.log10() + 
  scale.y.log10() + 
  geom_line() + 
  geom_point()

print(g)
```
